%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{verbatim}
\usepackage{color,hyperref}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}


\name{Vishwesh Jatala} % Your name



\address{Email:  \href{mailto:vishwesh@iitbhilai.ac.in}{vishwesh@iitbhilai.ac.in} Homepage: \href{https://vishweshjatala.github.io/}{https://vishweshjatala.github.io/}} % Your phone number and email

\address{\parbox{0.9\linewidth}{%
		\centering 
		 {\vskip 3mm \large \textbf{Assistant Professor}} \\
		 Office: 401A, Department of CSE, IIT Bhilai\\
		 Permanent Campus, Kutelabhata
		 Bhilai, Durg - 491001, Chhattisgarh, India }
    }
%\address{\parbox{0.4\linewidth}}{Office: 4.120, 201 E 24th Street, The University of Texas at Austin\\, Austin, Texas, Zip Code: 78712, United States, Phone: +1 737-217-9808 } % Your address


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}
	Graphics Processing Units (GPUs), High-Performance Computing, Graph Neural Networks, Graph Analytics.
\end{rSection}


\begin{rSection}{Education}

{\bf Doctor of Philosophy} \hfill {\em July 2011 - Dec 2018} \\ 
Department of Computer Science \& Engineering \\
Indian Institute of Technology, Kanpur \\
CPI: 9.0/10 \\
Thesis Advisor: Prof. Amey Karkare

{\bf Bachelor of Technology} \hfill {\em July 2005 - May 2009}  \\
Department of Computer Science \& Engineering \\
Visvesvaraya National Institute of Technology, Nagpur \\
CPI: 9.23/10 (\textbf{Institute Medal})

\end{rSection}


\begin{rSection}{Professional Experience}
	\begin{itemize}
		\item Assistant Professor, \textbf{IIT Bhilai} \hfill {\em Aug 2020 - Present}
		\item Postdoctoral Fellow, \textbf{University of Texas at Austin}  \hfill {\em Jan 2019 - June 2020}
		\item Research Fellow, \textbf{University of Texas at Austin} \hfill{\em May 2018 - Dec 2018}
		\item Research Intern, \textbf{IBM India Research Laboratory} \hfill{\em May 2013 - July 2013}
		\item Member of Technical Staff, \textbf{Oracle India Pvt Ltd} \hfill{\em June 2009 - July 2011}
	\end{itemize}
\end{rSection}


\begin{rSection}{Publications}
\begin{enumerate}

\item LSTC: Large-Scale Triangle Counting on Single GPU, Kishan Tamboli, \textbf{Vishwesh Jatala}, ACM/SPEC International Conference on Performance Engineering \textbf{(ICPE)}, 2026
\item GPU-Accelerated Time Series Anomaly Detection using Matrix Profile, Raviteja Nandam, \textbf{Vishwesh Jatala}, International Conference on Data Science \textbf{(IKDD CODS)}, 2025
\item Graph Coarsening for High-Performance GNN , Niharika Nayak, Kishan Tamboli, \textbf{Vishwesh Jatala} at Student Research Symposium, 32nd IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2025. \textbf{[Best SRS Poster Award]}
\item Edge Pruning Methods for Distributed GNN , Shrashank Maravi, Surendra Kumar Raut, Kishan Tamboli, \textbf{Vishwesh Jatala} at Student Research Symposium, 32nd IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2025.
\item CentGNN: A Centrality-Driven Scheme for High-Performance Graph Neural Networks , Surendra Kumar Raut, Kishan Tamboli, \textbf{Vishwesh Jatala} at Student Research Symposium, 32nd IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2025.	
\item Multivariate Time Series Data Mining for Failure Prediction \& Root Cause Analysis, Naman Agarwal, Gagan Raj Gupta, \textbf{Vishwesh Jatala}, Aniket Saha, IEEE International Conference on Acoustics, Speech, and Signal Processing \textbf{(ICASSP)}, 2025
\item A Cluster-Based Sampler for Fast GNN , Surendra Kumar Raut, Kishan Tamboli, \textbf{Vishwesh Jatala} at Student Research Symposium, 31st IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2024.
\item Accelerated Multilevel Graph Partitioning on GPUs, Amitesh Singh, Bhakti Dhorajiya, \textbf{Vishwesh Jatala} at Student Research Symposium, 31st IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2024.
\item A Partitioning Scheme for Large Scale Clique Counting on Single GPU, Vinayak Kesarwani, Shivangi Gaur, Sudeep Ranjan Sahoo, Kishan Tamboli, \textbf{Vishwesh Jatala} at Student Research Symposium, 31st IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2024.		
\item Distributed Graph Neural Networks, Dhruv Deshmukh, Gagan Gupta, and \textbf{Vishwesh Jatala}, Tutorial Track, Joint International Conference on Data Sciences and Management of Data \textbf{(CODS-COMAD)}, 2024
\item  Dhruv Deshmukh, Gagan Gupta, Manisha Chawla, \textbf{Vishwesh Jatala}, and Anirban Haldar, Entropy Aware Training for Fast and Accurate Distributed GNN, 23rd IEEE International Conference on Data Mining \textbf{(ICDM)}, 2023
\item Memory Efficient Sparse Matrix-Matrix Multiplication on GPU, Apurva Dogra, Kishan Tamboli, and \textbf{Vishwesh Jatala} at Student Research Symposium, 30th IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2023.
\item  Manohar Lal Das, \textbf{Vishwesh Jatala}, and Gagan Raj Gupta, Joint Partitioning and Sampling Algorithm for Scaling Graph Neural Networks, 29th IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2022.  
\item David P. Bunde, Kishwar Ahmed, Sridevi Ayloo, Tisha Brown-Gaines, Joel Fuentes, \textbf{Vishwesh Jatala}, Ruth Kurniawati, I\c{s}ıl $\ddot{O}$z, Apan Qasem, Philip J. Schielke, Mary C. Tedeschi, Thomas Y. Yeh, Adopting Heterogeneous Computing Modules: Experiences from a ToUCH Summer Workshop,10th Workshop on Education for High-Performance Computing \textbf{(EduHPC-22)}, 2022. 
\item Niharika Nayak, \textbf{Vishwesh Jatala}, Accelerating Graph Neural Networks using GPU, at Student Research Symposium \textbf{(SRS)}, 29th IEEE International Conference on High Performance Computing, Data, and Analytics \textbf{(HiPC)}, 2022.
\item Hochan Lee, David Wongy, Loc Hoang, Roshan Dathathri, Gurbinder Gill, \textbf{Vishwesh Jatala}, David Kucky, and Keshav Pingali, A Study of APIs for Graph Analytics Workloads, in IEEE International Symposium on Workload Characterization \& Distributed Processing Symposium \textbf{(IISWC)}, 2020.
\item \textbf{Vishwesh Jatala}, Roshan Dathathri, Gurbinder Gill, Loc Hoang, V Krishna Nandivada, Keshav Pingali, A Study of Graph Analytics for Massive Datasets on Large-Scale Distributed GPUs, in 34th IEEE International Parallel \& Distributed Processing Symposium (\textbf{IPDPS}), 2020. %(\textit{To appear}).
\item Roshan Dathathri, Gurbinder Gill, Loc Hoang, Hoang-Vu Dang, \textbf{Vishwesh Jatala}, V Krishna Nandivada, Marc Snir, Keshav Pingali, Gluon-Async: A Bulk-Asynchronous System for Distributed and Heterogeneous Graph Analytics, in ACM/IEEE International Conference on Parallel Architectures and Compilation Techniques (\textbf{PACT}), 2019 \textbf{[Nominated for Best Paper]}.
\item Loc Hoang*, \textbf{Vishwesh Jatala*}, Xuhao Chen, Udit Agarwal, Roshan Dathathri, Gurbinder Gill, Keshav Pingali, DistTC: High Performance Distributed Triangle Counting, in IEEE High Performance extreme Computing Conference (\textbf{HPEC}), 2019.  [* Both authors contributed equally] \textbf{[Student Innovation Award]}.
\item \textbf{Vishwesh Jatala}, Jayvant Anantpur, and Amey Karkare, Reducing GPU Register File Energy, in 24th International European Conference on Parallel and Distributed Computing (\textbf{Euro-Par}), 2018. 
\item \textbf{Vishwesh Jatala}, Jayvant Anantpur, and Amey Karkare, GREENER: A Tool for Improving Energy Efficiency of GPU Register File, in High Performance Computing, Data, and Analytics, Student Research Symposium (\textbf{HiPC, SRS}), Jaipur, India, 2017 \textbf{[Best Poster Award]}. 
\item \textbf{Vishwesh Jatala}, Jayvant Anantpur, and Amey Karkare, Scratchpad Sharing in GPUs, in ACM Transactions on Architecture and Code Optimization (\textbf{TACO}), 2017. 
\item \textbf{Vishwesh Jatala}, Jayvant Anantpur, and Amey Karkare, Improving GPU Performance Through Resource Sharing, 25th Symposium on High-Performance Parallel and Distributed Computing (\textbf{HPDC}), Kyoto, Japan, 2016.
\item \textbf{Vishwesh Jatala}, Jayvant Anantpur, and Amey Karkare, Resource Sharing for GPUs, Code Generation and Optimization (\textbf{CGO}, Poster Track), Barcelona, Spain, 2016.
%\item \textit{Vishwesh Jatala}, Jayvant Anantpur, and Amey Karkare,  GREENER: A Tool for Improving Energy Efficiency of Register Files, CoRR, https://arxiv.org/abs/1709.04697, 2017. 
\end{enumerate}
\end{rSection}


\begin{rSection}{Technical Reports}
\begin{itemize}
\item \textbf{Vishwesh Jatala}, Loc Hoang, Roshan Dathathri, Gurbinder Gill, V Krishna Nandivada, Keshav Pingali, An Adaptive Load Balancer For Graph Analytical Applications on GPUs, Arxiv, 2019. 
\end{itemize}
\end{rSection}


\begin{rSection}{Sponsored Research Projects}
	\begin{itemize}
		\item \textbf{Vishwesh Jatala}, A High-Performance and Memory Efficient Graph Analytical Framework for GPUs. Project Fund: $\sim$30 Lacs. Funding Agency: DST/SERB. 2021-23.
		\item \textbf{Vishwesh Jatala}, A High-Performance and Memory-Efficient Deep Learning Framework for GPUs. Project Fund: $\sim$12 Lacs. Research Initiation Grant. IIT Bhiai. 2022-25.
		\item Gagan Raj Gupta, \textbf{Vishwesh Jatala (Co-PI)} Digital Transformation System For Pre-Failure Alert Generation For Equipment Failture \& Cobble Reduction Based on Data Analytics And Video Analytics at BRM . Project Fund: 2.99 Crore, Bhilai Steel Plant, 2023-25.
		%\item Dr. Dhiman Saha, \textbf{Dr. Vishwesh Jatala}, Mr. Manish Kumar Verma, Dr. R. Kabaleeswaran, QryptoSafe: Lightweight \& High-Performance Implementation of Post-Quantum Cryptography Standard Algorithms with Indigenously Developed Secure Element, DST, 13 Cr (MPI) [\textbf{Submitted in 2024, Under review}]
	\end{itemize}
\end{rSection}

\begin{rSection}{Teaching}
	\begin{enumerate}
	\item CS516: Parallelization Of Programs
	\item CSL302: Compiler Design
	\item 	CS519: High Performance Computer Architecture
	\item 	CS251: Introduction to Language Processing
	\item 	CS501: Computer Systems
	\item 	CSP203: Software Tools \& Technolgies Lab
	\item 	CSL503: Computer Systems Engineering [Jointly with Prof. Santosh Biswas]
	\item 	CS100: Software Tools \& Technolgies Lab 1
	\item 	CS300: Principles of Programming Languages [Jointly with Dr. Subhajit Sidhanta]
	\item 	MAL505: Database Management Systems [Jointly with Dr. Souradyuti Paul]
	\item DSP505: Programming Lab for Data Science and Artificial Intelligence
	\item TPL616: Advanced Programming for DSAI [Jointly with Dr. Gagan Raj Gupta]
	\item 	Online Student Training Programme (STP) On Compiler Design, Organized by CSVTU and IIT Bhilai (March 21-25 2021)
	\item  Mathematics for Data Science, AICTE-QIP-PG CERTIFICATE PGROGRAMME, IIT Bhilai, 2024
	\end{enumerate}
\end{rSection}

\begin{rSection}{Student Mentoring}
	\begin{itemize}
		\item \textbf{Ph.D:}
		\begin{itemize}
			\item Niharika Nayak
			\item Surendra Kumar Raut
			\item Kishan Tamboli
			\item Yash Raj Verma			
		\end{itemize}
		\item \textbf{M.Tech:}
		\begin{itemize}		
			\item Gobardhan Meher 
			\item Rupam Roy 
			\item Aniket Mittal 
			\item Shrashank Maravi 
			\item Raviteja Nandam  (Graduated in 2025)
			\item Amitesh Singh (Graduated in 2025)
			\item Ranjith Vutnoor (Graduated in 2023)
			\item Apurva Dorga  (Graduated in 2023)
		\end{itemize}
		\item \textbf{M.Sc:}
		\begin{itemize}
			\item Karan Dewangan [Jointly with Dr. Avijit Pal] (Graduated in 2025)
			\item Himanshu [Jointly with Dr. Kuldeep Kumar Kataria]
		\end{itemize}
	\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	ACADEMIC ACHIEVEMENTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards}
	\begin{enumerate}
		\item Recipient of \textbf{Best Poster (SRS) Award} at HiPC 2025
		\item Recipient of Student Innovation Award in HPEC 2019
		\item Recipient of \textbf{Student Innovation Award} in HPEC, 2019
		\item \textbf{Nominated for Best Paper Award} in PACT, 2019
		\item Recipient of \textbf{Tata Consultancy Services (TCS) Ph.D. Fellowship} from Jan 2014 to June 2018.
		\item Recipient of \textbf{Best Poster Award} in HiPC, Student Research Symposium, 2017
		\item Recipient of \textbf{Best Poster Award} in IBM Research Day, IIT Kanpur, 2017
		\item Recipient of \textbf{Institute Medal} for academic excellence in B.Tech, CSE, VNIT Nagpur, 2009.
		\item Awarded \textbf{Academic Excellence Prize} for academic excellence in B.Tech, CSE, VNIT Nagpur, 2009.
		\item Recipient of \textbf{Dr.V.M. Dokras Felicitation Committee Prize} for academic excellence in $3^{rd}$ year B.Tech, CSE, VNIT Nagpur, 2008.
		\item Recipient of \textbf{Academic Excellence Prize} for academic excellence in $3^{rd}$ year B.Tech, CSE, VNIT Nagpur, 2008.
		\item Recipient of \textbf{Dr.S.G.Ghangrekhar Prize} for excellence in Mathematics in B.Tech, VNIT Nagpur, 2006
	\end{enumerate}
\end{rSection}


\begin{rSection}{Talks/Presentations}
\begin{itemize}
\item \textit{HPC Technologies for AI/ML}, FDP on The Role of Data Science in Computational Mathematics \& Statistics, 2025
\item \textit{HPC Technologies for AI/ML}, ATAL FDP, 2024
\item \textit{High Performance Distributed Graph Neural Networks}, NSM HPC Research Week, IIT Madras, November 2023
\item \textit{Graphics Processing Units, Guest Lecture}, G. H. Raisoni College of Engineering, 2022
\item \textit{Introduction to Parallel Architectures}, NSM-Computer Architecture Winter School (NSM-CAWS), 2021
\item \textit{GPU Architectures and CUDA Programming}, NSM-Computer Architecture Winter School (NSM-CAWS), 2021	
\item \textit{Graph Processing on GPUs}, at HiPC Programming Contest (GPU Track), 2021
\item \textit{Introduction to GPUs, CUDA Programming, Optimizations, and Research Directions}, at Computer Architecture Winter School (CAWS), 2020
\item \textit{Scratchpad Sharing in GPUs}, at 12th Inter-Research-Institute Student Seminar in Computer Science (IRISS), Nagpur, Feb 2018. 
\item \textit{Scratchpad Sharing in GPUs}, CSE Doctoral Symposium, NIIT University, Rajasthan, September 23rd-24th, 2017.
\item Poster Presentation on \textit{Resource Sharing for GPUs}, IBM Research Day, IIT Kanpur, April 2017. \textbf{[IBM Best Poster Award]} 
\item \textit{Improving GPU Performance Through Resource Sharing}, 11th Inter-Research-Institute Student Seminar in Computer Science (\textbf{IRISS}), Kolkata, Jan 2017.
\item Poster Presentation on \textit{Resource Sharing for GPUs}, Technology Day, IIT Kanpur, May 2016. 

\end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
%	Professional Service
%----------------------------------------------------------------------------------------
 
\begin{rSection}{Professional Service}
\begin{itemize}	
	\item \textbf{2025:}
	\begin{itemize}	
		\item Program Committee, HiPC 2025
		\item Program Committee, ICFEC 2025
		\item SRS Co-Chair, HiPC 2025
		\item External examiner, PhD Thesis, IIIT Hyderabad
		\item External examiner, MS Thesis, IIT Madras
	\end{itemize}
	
	\item \textbf{2024:}
	\begin{itemize}	
		\item Program Committee, HiPC 2024
		\item Poster Co-Chair, HiPC 2024
		\item Reviewer, TACO, 2024
		\item External examiner, for PhD Thesis, IIT Madras
		\item External examiner, for PhD Proposal Defense, IIIT Hyderabad
		\item External examiner, M.S Thesis, IIT Palakkad
	\end{itemize}
	\item \textbf{2023:}
	\begin{itemize}	
		\item Program Committee, HiPC 2023	
		\item Publicity Co-Chair, HiPC 2023
	\end{itemize}
	\item \textbf{2022:}
	\begin{itemize}	
		\item Program Committee, WDFHC 2022	
		\item Publicity Co-Chair, HiPC 2022
		\item Reviewer, JPDC 2022
	\end{itemize}
	\item \textbf{2021:}
	\begin{itemize}
		\item Organizing Committee, NSM-CAWS 2021		
		\item Publicity Chair, HiPC 2021
		\item Organizing Committee, HiPC Programming Contest (GPU Track)
		\item Organizing Committee, PPEE 2021
		\item Reviewer, JPDC
		\item Member of Master Thesis Evaluation Committee of a Student, NTNU
	\end{itemize}
	\item \textbf{2020:}
	\begin{itemize}
		\item Program Committee, PPoPP Artifact Evaluation
		\item Organizing Committee, CAWS 2020
		\item Reviewer, PACT and IPDPS (Joint reviewer)
		\item Member of Master Thesis Evaluation Committee of a Student, NTNU
	\end{itemize}
	\item  \textbf{2019:}
	\begin{itemize}
		\item Reviewer, PACT
		\item Member of Master Thesis Evaluation Committee of a Student, NTNU
	\end{itemize}
	\item  \textbf{2017:}
	\begin{itemize}
		\item Reviewer, HiPC SRS and ICCI
	\end{itemize}
	\item  \textbf{2016:}
	\begin{itemize}
		\item Reviewer, TOPC
	\end{itemize}
\end{itemize}
\end{rSection}



\begin{comment}


%----------------------------------------------------------------------------------------
%	Ph.D Thesis
%----------------------------------------------------------------------------------------

\begin{rSection}{Ph.D Thesis}{\hspace{6 mm}   \textit{Thesis Supervisor : Prof. Amey Karkare, Department of CSE, IIT Kanpur }}

\begin{itemize}
\item \textbf{Title:} Hardware and Software Optimizations for GPU Resource Management
%\textbf{Abstract:} Graphics Processing Units (GPUs) provide lot of opportunities for parallelization. Recently, they have been used for general purpose computations in addition to graphic computations. And GPUs can provide large benefits when they are used for data processing frameworks/languages such as MapReduce and SQL since they possess lot of parallelism. However, manual parallelization involves an overhead in optimizing for GPU architecture. To reduce this, we propose an auto parallelization framework for MapReduce which can be efficiently executed on GPU.
\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Past Work Experience}
\begin{itemize}

\item \begin{rSubsection}{IBM India Research Laboratory}{\textit{May 2013 - July 2013}}{Research Intern}{New Delhi}
\textit{Project Title}: Reliable Multicast using Software Defined Networking 
%In this project, we provided reliability service for group communication. The project extends Avalanche multi-cast routing algorithm by supporting reliability using pragmatic general multicast (PGM) protocol.
\end{rSubsection}


%\item \begin{rSubsection}{IIT Kanpur}{\textit{Aug 2011 - July 2012}}{System Administrator}{Kanpur}
%The project duties involve in resolving departmental network and computer laboratory issues. 
%\end{rSubsection}

\item \begin{rSubsection}{Oracle India Pvt Ltd}{\textit{June 2009 - July 2011}}{Member of Technical Staff}{Hyderabad}
The aim of our project is to find the security vulnerabilities in a product and provide best possible solutions to make it secure.
\end{rSubsection}


\end{itemize}
\end{rSection}


\begin{rSection}{Teaching Assistant}
%Designing course assignments, mentoring students for course projects, grading. \\
\begin{tabular}{ll}
CS738: Advanced Compiler Optimizations & CS335: Compiler Design \\ 
CS601: Mathematics for Computer Science & CS220: Introduction to Computer Organization \\  
CS252: Computing Laboratory & CS639: Program Analysis, Verification and Testing\\
NPTEL: Fundamentals of Database System &   CS602: Design and Analysis of Algorithms  \\
Workshop on C Programming \& Data Structures 
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Open Source Simulators/Tools & GPGPU-Sim, GPU Ocelot, Cetus, GPUWattch \\
& CACTI, McPAT, Soot, Lex, Yacc, PIN \\
Programming Languages & C, C++, Java, and Pascal \\
Assembly Level Languages & PTX and MIPS\\
Scripting Languages &  Perl Script and Shell Script\\
Parallel Programming & CUDA, OpenMP, and MPI \\
Network	Programming & RPC, RMI, and  Sockets \\
Query Languages & SQL, LINQ, and SPARQL\\
%Web Designing & HTML and PHP\\
\end{tabular}


\end{rSection}



%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------


%\begin{rSection}{References}

%\begin{itemize}
%\item Prof. Amey Karkare, Associate Professor, Department of CSE, IIT Kanpur, Kanpur, India. \\
%Email: karkare@cse.iitk.ac.in, Phone: +91 512 259 7520
%\item Prof. Keshav Pingali, Professor, Department of CS, The University of Texas at Austin, USA. \\
%Email: pingali@cs.utexas.edu, Phone: +1 512 232 6567
%%\item Prof. Mainak Chaudhuri, Associate Professor, Department of CSE, IIT Kanpur, Kanpur, India. \\
%Email: mainakc@cse.iitk.ac.in, Phone: +91 512 259 7890
%\item Prof. V. Krishna Nandivada, Associate Professor, Department of CSE, IIT Madras, India. \\
%Email: nvk@iitm.ac.in, Phone:  +91-44-2257-4380
%\item Dr. Jayvant Anantpur, Staff Engineer, Mentor Graphics Inc, Portland, USA. \\
%Email: jayvant.anantpur@gmail.com, Phone: +1 503 410 6637
%\end{itemize}

%\end{rSection}

%\pagebreak


%----------------------------------------------------------------------------------------
%	ACADEMIC PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Course Projects}

\begin{itemize}
\item \textbf{B.Tech Project: Automatic Number Plate Detection System using HTM}  \\
%\textbf{Description:} 
In this project, we implemented a number plate recognition system which can extract registration number from the image of a vehicle that is located at a suitable distance from a camera. We used image processing techniques to extract the number plate from the image, and recognized the characters in the number plate using hierarchical temporal memory (HTM).
\item \textbf{CS622: Cache Replacement Policy using Future and Reuse Distance}  \\
%\textbf{Description:}
LRU cache replacement policy fails to minimize cache misses when applications do not support temporal locality. To minimize the cache misses, we propose an approach that emulates the optimal replacement policy by introducing future and reuse distance in the cache.
\item  \textbf{CS738: Implementing Higher Level Loop Optimizations} \\
%\textbf{Description:}
We implemented the following loop optimizations for parallelizing loops in a program: loop interchange, loop skewing, loop reversal, and loop selection.
\item \textbf{CS618: Semantic Searching Technique in Temporal Database} \\
%\textbf{Description:}
Semantic searching techniques yield better results than the syntactic searching techniques. In this project, we implemented a technique to semantically search for given text from a temporal database. The proposed implementation uses RDF graph to represent the temporal information and uses R* tree to index the given the data.
\item \textbf{CS632: Distributed Storage System for Mobile Devices} \\
%\textbf{Description:}
In this project, I proposed an approach for distributed storage system in mobile devices and retrieval of data from the system even in the presence of failure of nodes. The proof of concept is verified by developing a utility, Distributed Phone Book. 
\end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EXTRA CURICULAR ACTIVITIES
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra Curricular Activities}

\begin{itemize}
\item Organizing member for the event of \textit{Paper Presentation} in AXIS-2006 at VNIT Nagpur
\item Participated in the event of \textit{Contraption} in AXIS-2006 at VNIT Nagpur
\item Participated in gaming event of \textit{IBM Software Context} in AXIS-2006 at VNIT Nagpur
\item Finalist in the event of \textit{Algo-Rhythm} in AXIS-2008  at VNIT Nagpur
\end{itemize}
\end{rSection}

\end{comment}





\end{document}
